Impact of Education on Entrepreneurship - Data Gathering and Analysis

### 2014-11-21 GEMDataSource.Rmd
Import NES 2010

>>>>

# Import GEM supportive teaching data as a proxy for how favourable to self-confidence a given education system is
SupportiveTeaching <- repmis::source_data("https://https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/NES2010CSV/2010GEMNES-Table%201.csv", header = TRUE, cache = FALSE)
